A Case Study in Preserving a High Energy Physics Application

### 2014-03-03 paper.tex
CMSSW size modification and verification

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 1.16TB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 181.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same trend occurs to the size of software and
other dependencies. The size of CMSSW repository is 1.16TB, the size of
packages checked out from CMSSW is 448.3MB, and the size of actually used CMSSW
files is only 6.3MB. 
The total size of PanFS mounted as {\tt /pscratch} is 155TB, however, the really used data from {\tt /pscratch} is only 1.6MB.
The third column of Table~\ref{table:size-original-real} illustrates the size of actually used data and software from each dependency.

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & hdfs & 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & http & 52MB & 51MB & 51MB \\ \hline
        .h file       & http & 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

Even if the orginal data size referred by the program is astonishing, the size
of really used data and software is greatly smaller.
Figure~\ref{fig:data-code-size} illustrates the inputs of the tau roast program.
After the TauAnalysis procedure, the data size of Ntuples is 43.3GB, however, the atual size of really used
data in the program is 20GB.  The same trend occurs to the size of software and
other dependencies. The size of CMSSW repository is 13.1GB, the size of
packages checked out from CMSSW is 448.3MB, and the size of actually used CMSSW
files is only 6.3MB. 
The total size of PanFS mounted as {\tt /pscratch} is 155TB, however, the really used data from {\tt /pscratch} is only 1.6MB.
The third column of Table~\ref{table:size-original-real} illustrates the size of actually used data and software from each dependency.
